Data Management for LSST Special Programs

### 2023-10-18 sec_proc.tex
updated thru UGP

Users will have access to the LSST Science Pipelines and data processing 
infrastructure, as well as dedicated computational resources next-to-the-data, 
via the Rubin Science Platform; \citeds{lse-319}.
Details of the planned ``User Batch" facility for data processing are described in 
\citeds{dmtn-202}.
Very computationally intense user processing might require external resources.

It is expected that some User-Generated pipelines and data products 
might be ``adopted" or ``federated" into the LSST Science Pipelines and the Prompt 
and Data Release data products, however, details regarding the federation of 
user-generated data products are to be provided elsewhere.

\textbf{A note prompt processing and alert production -- }
As the latency on processed visit image availability has an 80-hour
embargo, no user-generated pipeline will be able to process Special Programs 
data on a timescale similar to prompt processing and alert production 
(60 seconds to 24 hours).
No user-generated pipeline may contribute alerts to the LSST alert stream on 
any timescale.

Appendix~\ref{sec:spcs} provides more detailed, step-by-step data processing examples 
for some potential Special Programs as further illustration.

@@

User-generated data products might include, for example, DDF images coadded on custom 
timescales (e.g., weekly, monthly), or coadded using algorithms outside of the LSST 
Science Pipelines.

@@

Short-exposure images obtained during twilight, which will have a very bright sky 
background unlike other LSST images, might require user-generated algorithms to 
subtract the high sky background.

Short-exposure images obtained during the night would have fewer stars for 
astrometric and photometric calibration, and might require user-generated 
processing pipelines.

@@

Mini-surveys with time-domain science goals that aren't met by the Prompt pipelines, 
e.g., those that require difference imaging with coadded images on an intermediate 
timescale (e.g., a weekly stack), would require user-generated processing.

>>>>

\textbf{Computational resources -- }
Users will have access to the LSST Science Pipelines and data processing 
infrastructure, as well as dedicated computational resources next-to-the-data, 
via the Rubin Science Platform; \citeds{lse-319}.
Details of the planned ``User Batch" facility for data processing are described in 
\citeds{dmtn-202}.
Very computationally intense user processing might require external resources.

\textbf{Adopting user code or data products --}
It is expected that some User-Generated pipelines and data products 
might be ``adopted" or ``federated" into the LSST Science Pipelines and the Prompt 
and Data Release data products.
Details regarding this are to be provided elsewhere.

\textbf{Alert production is restricted -- }
User-Generated Processing will not be able to release alert packets in the LSST alert stream.
As the latency on processed visit image availability has an 80-hour
embargo, no user-generated pipeline will be able to process Special Programs 
data on a timescale similar to prompt processing and alert production 
(60 seconds to 24 hours).
Thus, no User-Generated Processing may contribute alerts to the LSST alert stream on 
any timescale.

Further examples of User-Generated Processing are provided below.

@@

User-Generated Processing and data products might include, for example, DDF images coadded 
on custom timescales (e.g., weekly, monthly), or coadded using algorithms outside of the 
LSST Science Pipelines.

@@

Short-exposure images obtained during twilight, which will have a very bright sky 
background unlike other LSST images, might require specialized algorithms
to subtract the high sky background which are not available in the LSST Science Pipelines,
and might require User-Generated Processing.

Short-exposure images obtained during the night might have too-few stars to satisfy the
astrometric and photometric calibration routines in the LSST Science Pipelines,
and might require User-Generated Processing.

@@

Mini-surveys with time-domain science goals that aren't met by the Prompt pipelines, 
e.g., those that require difference imaging with coadded images on an intermediate 
timescale (e.g., a weekly stack), would require User-Generated Processing.
